%------------------------
% Shen Ruililin Résumé (Compact, per user specs)
% Base = original template + GPA, Laidlaw, Wu Zhi Qiao, Laidlaw award.
% Omitted: Upcoming; Tam Wun Tsun Horizons enrichment award.
% Layout lessons learned:
%   1) Never put long degree/GPA strings on the same heading row as right-aligned dates.
%   2) Awards tabularx left column must be p{...} with @{\hspace{...}} gutter ---
%      plain l + long titles collapses the X column and years collide (Scholarship2025-26).
%   3) Do not stack aggressive negative \vspace with tight itemsep --- that causes
%      heading/bullet line bleed. Prefer shorter copy over crushing vertical space.
%   4) Keep \cvheading role titles short so they do not collide with right-aligned dates.
% Compile: tectonic -X compile ShenRuililin_CV.tex  OR  pdflatex ShenRuililin_CV.tex
% Note: 10pt (was 11pt) so Laidlaw + Wu Zhi Qiao fit on one page without crushing
%       vertical space into bleed.
%------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{newpxtext}
\usepackage{ragged2e}
\linespread{1.04}
\usepackage[T1]{fontenc}

\providecommand{\textopenbullet}{\ensuremath{\circ}}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.55in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}
% \pdfgentounicode=1 % pdfLaTeX only

\newcommand{\cvitem}[1]{\item\small{#1}}
\newcommand{\cvheading}[4]{
  \vspace{0.5pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-1pt}
}
\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}, itemsep=2.5pt, parsep=0pt, topsep=1pt]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}[label=\textopenbullet, leftmargin=12pt, itemsep=1pt, parsep=0pt, topsep=1pt]\justifying}
\newcommand{\cvitemend}{\end{itemize}}

\begin{document}

%------------- CONTACT -------------
\begin{center}
  {\LARGE\bfseries Shen Ruililin} \\
  \vspace{1pt}\small
  \href{mailto:bobshenruililin@gmail.com}{bobshenruililin@gmail.com}\ $\diamond$\
  \href{mailto:shenrll@connect.hku.hk}{shenrll@connect.hku.hk}\ $\diamond$\
  +852 5573 6530\ $\diamond$\
  \href{https://www.linkedin.com/in/shenruililin/}{linkedin.com/in/shenruililin}
\end{center}

%------------- INTRODUCTION (no subtitle) -------------
\vspace{1pt}
Passionate, resourceful, and driven student with contributions in academia, health, and technology. Interdisciplinary background across the natural sciences, social innovation, and language; eager to collaborate in teams that create significant, positive change.

%------------- EDUCATION -------------
\section{Education}
\cvheadingstart
  \cvheading
    {The University of Hong Kong}{Hong Kong SAR}
    {BASc in Global Health and Development, HKUMed}{2025 -- 2029}
  \cvitemstart
    \cvitem{Year \mbox{GPA} 4.24/4.30. Interdisciplinary public health, global policy, and social innovation. \textbf{St.\ John's College} (2025--): top-50 selective residential college.}
  \cvitemend
  \cvheading
    {Po Leung Kuk Choi Kai Yau School}{Hong Kong SAR}
    {IBDP 41/45 \textbar\ IGCSE 8A*, 2A}{2019 -- 2025}
  \cvitemstart
    \cvitem{\textbf{Class Monitor} (2022--25); \textbf{Co-founder / Student Leader, Medical Club} (2023--24): healthcare sessions, career tasters, CPR; membership to 80+.}
  \cvitemend
\cvheadingend

%------------- EXPERIENCE -------------
\section{Selected Experiences}
\cvheadingstart
  \cvheading
    {Laidlaw Scholars Programme, HKU}{Hong Kong SAR}
    {Undergraduate Research Scholar}{Jan 2026 -- Present}
  \cvitemstart
    \cvitem{Heat and cardiovascular admissions among older adults (Hospital Authority data) with Prof.\ David Bishai; dual-season preparedness and heat--health surveillance.}
  \cvitemend

  \cvheading
    {HKU Wu Zhi Qiao / Horizons Programme}{Mainland China}
    {Student Coordinator; Gannan Horizons fieldwork}{Mar 2026 -- Jun 2026}
  \cvitemstart
    \cvitem{Completed Mainland rural health and infrastructure service as student coordinator (May--Jun), after Gannan Horizons fieldwork (Mar) on livelihoods and trust.}
  \cvitemend

  \cvheading
    {Hong Kong Laureate Forum}{Hong Kong SAR}
    {Forum Ambassador}{Sep 2025 -- Nov 2025}
  \cvitemstart
    \cvitem{Coordinated with 20+ Shaw Laureates, young scientists, and the HKLF Secretariat; showcased Cantonese culture and GBA innovation during the Forum.}
  \cvitemend

  \cvheading
    {Asian Spring Program on Rationality}{Taoyuan, Taiwan}
    {Fully-funded Scholar}{Feb 2025}
  \cvitemstart
    \cvitem{1 of 20 selected globally for a 10-day program on game theory, Bayesian inference, and Fermi estimation.}
  \cvitemend

  \cvheading
    {Hong Kong Observatory and PolyU MicroLARGE Lab}{Hong Kong SAR}
    {Research Intern, Junior Researcher Mentoring Programme}{Feb 2024 -- Jul 2024}
  \cvitemstart
    \cvitem{Modeled DeepMind GraphCast integration into Hong Kong forecasting (Beidou-related optimizations); atmospheric rivers concept presented at AGU.}
  \cvitemend

  \cvheading
    {HKUST IAS Center for Quantum Technologies}{Hong Kong SAR}
    {Research Intern, Quantum Computing for Gifted Students Scheme}{Jul 2023 -- Mar 2024}
  \cvitemstart
    \cvitem{Built Qiskit quantum models and SpinQ auto-calibration routines; presented entanglement versus measurement research at physics seminars.}
  \cvitemend

  \cvheading
    {Massachusetts Institute of Technology}{Cambridge, MA, USA}
    {Youth Fellow, MIT Hong Kong Innovation Node}{Jul 2023 -- Sep 2023}
  \cvitemstart
    \cvitem{Prototyped MEDocGPT, an LLM healthcare chatbot and mobile app for early health intervention, with entrepreneurs, students, and clinicians.}
  \cvitemend
\cvheadingend

%------------- AWARDS -------------
\section{Selected Awards}
\vspace{1pt}
\begin{tabularx}{\textwidth}{@{}>{\bfseries\raggedright\arraybackslash}p{2.3in}@{\hspace{8pt}}>{\raggedright\arraybackslash}X@{}}
Laidlaw Scholars Programme & \small Undergraduate Research \& Leadership Scholarship, 2025--26 \\[1pt]
Hong Kong Young Writers' Award & \small 2024 Bauhinia Club Award for Creative Writing \textbar\ 1st/1400+ \\[1pt]
IYPT (Hong Kong) & \small 2022 Champion \textbar\ 1st/16;\quad 2021 1st Runner-up \textbar\ 2nd/8 \\[1pt]
World Scholars' Cup & \small 2023 HK Round Champion \textbar\ 1st/200+;\quad Bangkok Global Round 13th/300+ \\[1pt]
AI Formula Edge Racing & \small 2023 Hong Kong Champion \textbar\ 1st/30+;\quad Greater Bay Area Champion \textbar\ 1st/50+ \\
\end{tabularx}

\end{document}
